Long-term Water Quality Change in Rhode Island Lakes and Ponds

### 2019-02-12 manuscript/manuscript.Rmd
changed method from kendalls tau to regression.  closes #12

### Kendall's Tau

Kendall's Tau and the Mann-Kendall test are commonly used to test for monotonic trends water quality data [@mann1945nonparametric; @helsel2002statistical; @hipel1994time].  We followed these standard procedures to test for postive or negative trends in lake temperature, chlorophyll *a*, total nitrogen, and total phosphorus.

>>>>

### Linear regression

Testing for a regression slope being different than zero can be used to test for monotonic trends in water quality data [@helsel2002statistical].  We used these standard procedures to test for postive or negative trends in lake temperature, chlorophyll *a*, total nitrogen, and total phosphorus.  For each parameter we fit a regression line to the z scores as a function of year and tested the null hypothesis that no trend existed (e.g. $\beta$~1~ = 0).
